25 years of Social Work Research

### 2015-03-23 dataCleaning.Rmd
Updated manuscript.

```{r initialization_dataprocessing}
rm(list=ls())   
# Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)

# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)

@@

```{r appendData, comment=NA, echo=FALSE}
appendData.f()

@@

```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE}
shortArticles.f()
```

```{r titleMatching, echo=FALSE}
titleMatching.f()

@@

```{r otherDocuments, echo=FALSE}
otherDocuments.f()
articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r final, comment=NA, echo=FALSE}
fewArticles.f()
articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r finalList, comment=NA, echo=FALSE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r plotArticleCount}
n.articles.year <- filter(full.df, attributes == "pubYear") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

@@

```{r plotJournalCount}
n.journals.year <- filter(full.df, attributes == "journal") %>%
    select(articleID, record)

@@

```{r plotAuthorCount}

@@

n_authors2 <- n_authors%>% 
       select(median.n, average.n, std.dev) %>%
       rename(median = median.n, average = average.n)

@@

```{r locationExtraction2}
LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, regex=indx.country)))[-2]
country.indexed <- as.numeric(rownames(countries.extracted))
location.ID <- LO.df2$articleID[country.indexed]

detach(package:stringi)
```

```{r locationWithtUS}
year.df <- filter(full.df, attributes == "pubYear") %>%
            select(articleID, record)

@@

```{r plotLocationWithUS}

@@

```{r nsf}
nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
colnames(nsf) <- c("n.grads", "years")
```

```{r nsfPlot}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

>>>>

```{r initialization}
rm(list=ls())  
load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")

# Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)
```

```{r eval=FALSE}
# Read data files
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
countries.csv <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/countries.csv")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
#load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
#hodge <- readLines("/Users/SSW/Documents/GitHub/SocialWork100Years/search_specifications/hodge.txt", n = -1)

@@

```{r appendData, comment=NA, echo=FALSE, eval=FALSE}
appendData.f()

@@

```{r shortArticles, comment=NA, echo=FALSE, warning=FALSE, eval=FALSE}
shortArticles.f()
```

```{r titleMatching, echo=FALSE, eval=FALSE}
titleMatching.f()

@@

```{r otherDocuments, echo=FALSE, eval=FALSE}
otherDocuments.f()
articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r final, comment=NA, echo=FALSE, eval=FALSE}
fewArticles.f()
articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r finalList, comment=NA, echo=FALSE, eval=FALSE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r plotArticleCount, eval=FALSE}
n.articles.year <- filter(full.df, attributes == "pubYear") 
year.split <- split(n.articles.year, n.articles.year$record)
year.count <- unlist(lapply(year.split, nrow))
year.count <- year.count[order(names(year.count))]
years <- names(year.count)

@@

```{r plotJournalCount, eval=FALSE}
n.journals.year <- filter(full.df, attributes == "journal") %>%
    select(articleID, record)

@@

```{r plotAuthorCount, eval=FALSE}

@@

n_authors2 <- n_authors%>% 
       select(median.n, average.n, std.dev) %>%
       rename(Median = median.n, Average = average.n, Standard_Deviation =std.dev)

@@

```{r locationExtraction2, eval=FALSE}
LO.df2 <- filter(full.df, attributes == "location" | attributes == "abstract" |
                 attributes == "article" | attributes == "keyword")
indx.country <- paste(countries.csv$x, collapse = "|")
library(stringi)
countries.extracted <- na.omit(within(LO.df2, text1<- stri_extract(LO.df2$record, regex=indx.country)))[-2]
country.indexed <- as.numeric(rownames(countries.extracted))
location.ID <- LO.df2$articleID[country.indexed]
detach(package:stringi)
```

```{r locationWithtUS, eval=FALSE}
year.df <- filter(full.df, attributes == "pubYear") %>%
            select(articleID, record)

@@

```{r plotLocationWithUS, eval=FALSE}

@@

```{r nsf, eval=FALSE}
nsf <- data.frame(c(238, 273, 304, 323, 308, 287, 338, 332, 308, 289, 280), as.factor(seq(2002,2012, 1)))
colnames(nsf) <- c("n.grads", "years")
```

```{r nsfPlot, eval=FALSE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
     scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
     ylab("Doctoral degrees") +
     xlab("Year") +
     geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1), 
           title = element_text(size = 10)) +
     ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

#save.image(file = "socialWorkHistory.Rdata")
